Ontology Matching Paper An ontology alignment over Amsterdam (Parking spots, events and activities)

### 2016-05-08 milestone3/paper/paper.tex
done body, missing abstract

% first the title is needed
\title{Ontology Matching Paper}

@@

In general, the problem of matching ontologies has been studied before by Semantic Web researchers. As Shvaiko et al. state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent us from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}. Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities, properties and instances. The Ontology Alignment Evaluation Initiative is an annual international competition that serves as an evaluation for state of the art alignment tools.

@@

\begin{enumerate}
	\item \textbf{OLA \cite{euzenat2004ontology}:} Developed in 2004, the OWL Lite Alignment (OLA) is a tool for automatic matching of ontologies that implements the OLA algorithm designed in collaboration by the DIRO, University of Montréal and INRIA Rhône Alpes. It participated in OEIA 2005 \cite{euzenat2005ola} and 2007 \cite{djoufak2007ola} and increased its own results from 0.80 to 0.89 in Precision, and 0.74 to 0.87 in Recall. At the time, it was one of the pioneers of ontology matching, yet no it is nowadays outdated.
	\item \textbf{S-Match \cite{giunchiglia2004s}:} S-Match is a semantic matching tool that is suitable for many applications. However, it is not specific for ontology matching and it has not participated in the latest OAEI.
	\item \textbf{MapONTO \cite{an2004refining}:} MapOnto, just as S-Match, is a general purpose semantic matcher. It is an Initiative from the University of Toronto and it is implemented as a plug-in for Protege. At first sight, this option seemed promising, however the latest release is compatible with obsolete versions of Protege. 
	%\item \textbf{WordNet:Similarity \cite{pedersen2004wordnet}:} Semantic 
	\item \textbf{AML \cite{faria2013agreementmakerlight}:} The Agreement
	Maker Light (AML) is the improved version of the original Agreement Maker. It is a simple, user-friendly application for matching ontologies which also provides visualization and evaluation of the alignment. Further details will be discussed in Section \ref{Ontology_Matching}.
\end{enumerate}

\section{Methods, Algorithms and Implementation}
% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
With the results from our Related Work research, we selected AML for ontology matching and SILK for ontology alignment. The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.

% Maybe you want to separate this part into subsections for your two systems
\subsection{Ontology Matching}
\label{Ontology_Matching}
Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML. This tool performed the best for lightweight ontologies, as measured in terms of F-measure. The reasons behind this choice are that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism. The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching. A lexical matching is always performed, followed by other metrics the user can choose from, ranging from structure to content based and others. Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
%examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.

@@

\subsection{Data Linkage}
In this section the developed Data Linkage system is presented.
It interlinks our dataset with two other datasets from groups 13 and 15. We
decided to implement the linking workflow and procedures using the
\textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions
itself as ``The Linked Data Integration Framework''. Silk is an open source
project for integrating heterogeneous data sources and among its use cases is
generating links between Linked Data sources, which is exactly within our needs.
Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual
editor for linkage rules.

@@

\subsubsection{Linking the Cultural Dataset}
This dataset has a domain in part similar to our so the linking procedure
is trivial and reduces to a check on the \texttt{rdfs:label} and some other
property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
that matches events; in this case the match is checked against
\texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create
15 links over 239 source and 479 target event entities.

@@

\subsubsection{Linking the Tourist Safety Dataset}
In spite being about a different domain, this dataset can still be linked with
ours for what concerns events and locations / venues. Indeed the overlap between
events in this dataset and ours is big and we are able to match a big proportion
of entities by using a linkage rule similar to that shown in Figure
\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
Using this linkage rule we are able to link 45 events and locations between the
two datasets.

\subsubsection{Linking the Activity Finding Dataset}
For events the linkage rule is less trivial and immediate than that for the
Cultural Dataset and involves the use of more properties and an aggregator as
shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to
link 84 activities / events.

@@

AML also has the ability to evaluate a certain match with respect to a reference match. This gives the option to the end user to manually force or evaluate the match and thus supervise and validate the final match. As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.

Hereby we report the results for the best matched alignments to the three selected ontologies. Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.

\subsection{Group 10: Cultural Ontology}
This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues.

@@

\subsection{Group 13: Tourist safety Ontology}
This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity.

@@

\subsection{Group 15: Activity finding Ontology}
In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies.

@@

\section{Results and Discussion}
% Give here details about the most important results of your experiments. Use tables and figures, but focus on the interesting and important results. Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings. Be explicit about your research question and hypothesis, and discuss they might be true, or false. 
From the previous section we conclude that the ontology for group 13 matches the best to our ontology since it has the highest number of matches with the least number of mismatches. Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).

Moreover, conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected. Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do. However, they model characteristics of events as Entities (such as Image, Description and Time Period), while we do it as Properties. To the best of our knowledge, AML cannot match entities to properties. This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent proper matching and alignment.

A different problem occurs in the case of the matching to the ontology of group 15. In this case, we found overmatching since their ontology has duplicate classes for Venue and Event. Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results. This matching required the most amount of work regarding experimenting and tuning of matching. As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.

@@

From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures.

Furthermore, our experience is backed up by the findings described in Section \ref{related_work}. As we see, Ontology matching is a growing field, that comes up with new promising tools every year. Yet, follow up is not consistent and a robust solution for automatic, or semi-automatic ontology matching has yet to be developed.

>>>>

% first the title is needed
\title{Ontology Matching Paper An ontology alignment over Amsterdam (Parking spots, events and activities)}

@@

In general, the problem of matching ontologies has been studied before by Semantic Web researchers. As Shvaiko et al. state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent us from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}. Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences in entities, properties and instances. The Ontology Alignment Evaluation Initiative is an annual international competition that serves as an evaluation for state of the art alignment tools.

@@

\begin{enumerate}
	\item \textbf{OLA \cite{euzenat2004ontology}:} Developed in 2004, the OWL Lite Alignment (OLA) is a tool for automatic matching of ontologies that implements the OLA algorithm designed in collaboration by the DIRO, University of Montréal and INRIA Rhône Alpes. It participated in OEIA 2005 \cite{euzenat2005ola} and 2007 \cite{djoufak2007ola} and increased its own results from 0.80 to 0.89 in Precision, and 0.74 to 0.87 in Recall. At the time, it was one of the pioneers of ontology matching, yet the project was abandoned and it is nowadays outdated.
	\item \textbf{S-Match \cite{giunchiglia2004s}:} S-Match is a semantic matching tool that is suitable for many applications. However, it is not specific for ontology matching and it has not participated in the latest OAEI.
	\item \textbf{MapONTO \cite{an2004refining}:} MapOnto, just as S-Match, is a general purpose semantic matcher. It is an initiative from the University of Toronto and it is implemented as a plug-in for Protege. At first sight, this option seemed promising, however the latest release is only compatible with obsolete versions of Protege. 
	%\item \textbf{WordNet:Similarity \cite{pedersen2004wordnet}:} Semantic 
	\item \textbf{AML \cite{faria2013agreementmakerlight}:} The Agreement
	Maker Light (AML) is the improved version of the original Agreement Maker. It is a simple, user-friendly application for matching ontologies which also provides visualization and evaluation of the alignment. Further details will be discussed in Section \ref{Ontology_Matching}.
\end{enumerate}

\section{Methods, Algorithms and Implementation}
% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
With the results from Section \ref{related_work}, we selected AML for ontology matching and SILK for ontology alignment. The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.

% Maybe you want to separate this part into subsections for your two systems
\subsection{Ontology Matching}
\label{Ontology_Matching}
Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML. This tool performed the best for lightweight ontologies, as measured in terms of F-measure \footnote{The F-measure is the harmonic mean of Precision and Recall.}. AML exceeded our expectations with regards to run time results, comprehensive user interface and integrated evaluation mechanism. The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching. A lexical matching is always performed as default, followed by other metrics the user can choose from, ranging from structure to content based and others. Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
%examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.

@@

\subsection{Data Linkage}
In this section the developed Data Linkage system is presented. It interlinks our dataset with the previously mentioned datasets from groups 10, 13 and 15. We decided to implement the linking workflow and procedures using the \textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions itself as ``The Linked Data Integration Framework''. Silk is an open source project for integrating heterogeneous data sources. Its use cases include generating links between Linked Data sources, which is exactly within our needs. Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual editor for linkage rules.

@@

\subsubsection{Linking Group 10: Cultural Ontology}
This dataset has a domain similar to ours so the linking procedure
is trivial and is reduced to a check on the \texttt{rdfs:label} combined with some other property. An example of a Silk linkage rule that matches Events is shown in Figure \ref{fig:link_event_g10}. In this case the match is checked against \texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create 15 links over 239 source and 479 target event entities.

@@

\subsubsection{Linking Group 13: Tourist safety Ontology}
In spite having a different domain, this dataset can still be linked to ours for what concerns events and locations / venues. Indeed the overlap between events in this dataset and ours is large. We are able to match a larger proportion of entities by using a linkage rule similar to that shown in Figure\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources. Using this linkage rule we are able to link 45 events and locations between the two datasets.

\subsubsection{Linking Group 15: Activity finding Ontology}
\label{link_g15}
This time the linkage rule for events is less trivial and immediate than that for the previous two datasets. As such, it involves the use of more properties and an aggregator as shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to link 84 activities / events.

@@

AML also has the ability to evaluate a certain match with respect to a reference match. This gives the option for the end user to manually force or evaluate the match and thus supervise and validate the final match. As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.

Hereby we report the results of evaluating the automatic matching procedure, as performed by AML, with the human validated alignment for the three selected ontologies. Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.

\subsection{Group 10: Cultural Ontology}
This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues. A visualization of the matching is presented in Figure \ref{fig:match_g10}.

@@

\subsection{Group 13: Tourist safety Ontology}
This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity. A visualization of the matching is presented in Figure \ref{fig:match_g13}.

@@

\subsection{Group 15: Activity finding Ontology}
In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies. A visualization of the matching is presented in Figure \ref{fig:match_g15}.

@@

\section{Results and Discussion}
% Give here details about the most important results of your experiments. Use tables and figures, but focus on the interesting and important results. Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings. Be explicit about your research question and hypothesis, and discuss they might be true, or false. 
From the previous section we observe that the ontology for group 13 has the highest number of matches (six) with the least number of mismatches (one). Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).

At the same time, the ontology for group 15 produces the same number of matches (six) but it has a high number of mismatches as well (six). Most of the mismatches come from Properties, since this particular ontology has a high degree of customizable properties with ambiguous names.

However, regardless of having the same number of matches, the ontology for group 15 led to a higher number of links to our ontology than for group 13. This is due to the higher overlap in instances that allows for a closer alignment.

A second observation is one made for the performance of matching with group 10. Conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected. Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do. However, they model characteristics of events as Entities (such as Image, Description and Time Period), while we do it as Properties. To the best of our knowledge, AML cannot match entities to properties. This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent proper matching and alignment.

A third observation regards a different problem occurring in the case of the matching to the ontology of group 15. In this case, we found overmatching since their ontology has duplicate classes for Museum, Venue and Event. Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results. This matching required the most amount of work regarding experimenting and tuning of matching, as well as alignment with SILK as mentioned in Section \ref{link_g15}. As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.

@@

From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures. Furthermore, our experience is backed up by the findings described in Section \ref{related_work}. As we see, Ontology matching is a growing field, that comes up with new promising tools every year. Yet, follow up is not consistent and a robust solution for automatic, or semi-automatic ontology matching has yet to be developed.
